Probabilities of polar aligned disks in binary star systems

### 2024-10-09 src/tex/ms.tex
Add eqs 32, 38 from ML19
Note that the ZL18 soln is recovered for j=0

\section{Analytic Treatment}
\label{sec:analytic}
For a massive ring that is misaligned to the binary orbit there are two conditions that determine if the ring is librating \citep[see Equations 31, 32, 38 in][]{martin2019}. Each condition is valid for a different regime of the constant of motion $\chi$ that is defined with
\begin{equation}
    \chi = e_{\rm b}^2 - 2\,(1 - e_{\rm b}^2)\,j\,(2j + \cos{i})
\end{equation}
for binary eccentricity $e_{\rm b}$, normalized ring angular momentum $j = J_{\rm r}/J_{\rm b}$, and mutual inclination $i$. \RGM{maybe include equations 32 and 38 in ML19 here?} These conditions can be rearranged to find the minimum value of $\Omega$ that will allow for a librating orbit.
\begin{equation}
    \label{eq:omega_min}
    \sin^2{\Omega_{\rm min}} = 
    \left \{
    \begin{array}{lr}
         \frac{(1-e_{\rm b}^2) (2j + \cos^2{i})}{5 e_{\rm b}^2 \sin^2{i}} & \text{if} ~\chi \ge 0 \\
    \frac{2}{5 \sin^2{i}} + \frac{\cos{i}}{5j \sin^2{i}} - \frac{e_{\rm b}^2}{20 j^2 (1-e_{\rm b}^2) \sin^2{i}} & \text{if} ~\chi < 0
    \end{array}
    \right .
\end{equation}

Since the range of $\sin^2{\Omega_{\rm min}}$ is $[0,1]$, there exists a critical value for the inclination, $i_{\rm crit}$, below which all orbits circulate. For the $\chi \ge 0$ case, we require
\begin{equation}
    \label{eq:icrit1}
    \frac{5 e_{\rm b}^2}{1-e_{\rm b}^2} \sin^2{i_{\rm crit}} - (\cos{i_{\rm crit}} + 2j)^2 = 0
\end{equation}
and for the $\chi < 0$ case, $i_{\rm crit}$ satisfies
\begin{equation}
    \label{eq:icrit2}
    \sin^2{i_{\rm crit}} - \frac{\cos{i_{\rm crit}}}{5j} + \frac{e_{\rm b}^2}{20 j^2 (1-e_{\rm b}^2)} + \frac{2}{5} = 0.
\end{equation}
If the left hand side of equation~(\ref{eq:icrit1}) or~(\ref{eq:icrit2}) (depending on the value of $\chi$) evaluates to $<0$, then only circulating orbits are possible.

>>>>

\section{Analytic Treatment}
\label{sec:analytic}
For a massive ring that is misaligned to the binary orbit there are two conditions that determine if the ring is librating \citep[see Equations 31, 32, 38 in][]{martin2019}. Each condition is valid for a different regime of the constant of motion $\chi$ that is defined with
\begin{equation}
    \chi = e_{\rm b}^2 - 2\,(1 - e_{\rm b}^2)\,j\,(2j + \cos{i})
\end{equation}
for binary eccentricity $e_{\rm b}$, normalized ring angular momentum $j = J_{\rm r}/J_{\rm b}$, and mutual inclination $i$. The condition for libration is
\begin{equation}
    \label{eq:lib_condition}
        \begin{array}{lr}
            -(1-e_\text{b}^2)(2j+\cos{i})^2 + 5e_\text{b}^2 \sin^2{i}\sin^2{\Omega} > 0 & \chi > 0 \\
            e_\text{b}^2 + 4j(1-e_\text{b}^2)(-\cos{i} + j(-2+5\sin^2{i}\sin^2{\Omega})) > 0 & \chi < 0 .
        \end{array}
\end{equation}
These conditions can be rearranged to find the minimum value of $\Omega$ that will allow for a librating orbit.
\begin{equation}
    \label{eq:omega_min}
    \sin^2{\Omega_{\rm min}} = 
    \left \{
    \begin{array}{lr}
         \frac{(1-e_{\rm b}^2) (2j + \cos^2{i})}{5 e_{\rm b}^2 \sin^2{i}} & \text{if} ~\chi \ge 0 \\
    \frac{2}{5 \sin^2{i}} + \frac{\cos{i}}{5j \sin^2{i}} - \frac{e_{\rm b}^2}{20 j^2 (1-e_{\rm b}^2) \sin^2{i}} & \text{if} ~\chi < 0
    \end{array}
    \right .
\end{equation}

Since the range of $\sin^2{\Omega_{\rm min}}$ is $[0,1]$, there exists a critical value for the inclination, $i_{\rm crit}$, below which all orbits circulate. For the $\chi \ge 0$ case, we require
\begin{equation}
    \label{eq:icrit1}
    \frac{5 e_{\rm b}^2}{1-e_{\rm b}^2} \sin^2{i_{\rm crit}} - (\cos{i_{\rm crit}} + 2j)^2 = 0
\end{equation}
and for the $\chi < 0$ case, $i_{\rm crit}$ satisfies
\begin{equation}
    \label{eq:icrit2}
    \sin^2{i_{\rm crit}} - \frac{\cos{i_{\rm crit}}}{5j} + \frac{e_{\rm b}^2}{20 j^2 (1-e_{\rm b}^2)} + \frac{2}{5} = 0.
\end{equation}
If the left hand side of equation~(\ref{eq:icrit1}) or~(\ref{eq:icrit2}) (depending on the value of $\chi$) evaluates to $<0$, then only circulating orbits are possible. Note that when $j=0$, $\chi \ge 0$ and equation (\ref{eq:omega_min}) recovers equation (75) from \citet{zanazzi2018}.
